Cover letter for the original IJRR submission

### 2017-05-09 body/results.tex
typos
car model is not polaris

\subsubsection{HRP-2 -- Polaris car egress (Figure~\ref{fig:car})}
In this scenario inspired from the DRC car egress HRP-2 has to step out of the Polaris car.

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/polaris}
  \caption{
           Selected frames from the polaris egress scenario. }
		   \label{fig:car}
\end{figure}

@@

\subsubsection{Discretization of the guide path} \label{sec:disc}
The discretization step is a user-defined, fixed parameter. The step
has an influence on the output of the planner: if too large steps are taken,
the planner may fail since we impose the constraint that only one contact change might occur
between two consecutive steps. On the other hand, a small step will not impact the success rate of the planner, 
but may generate unnecessary states. In most scenarios the torso of HRP-2 moves about 15 cm between two postures, but only 3 cm
for the car egress scenario to handle the geometry of the polaris.
For future work, we would like to automatically adapt the size of the discretization step to the complexity of the environment.

@@

\begin{table}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{35pt} | >{\centering\arraybackslash}m{35pt} | c}
  &  Equilibrium success rate & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs 	& 99.5\%  & 0.1\% 	& 0.4\% \\
   Standing up 		& 87.8\%  & 6.1\% 	& 6.1\% \\
   Car egress 		& 66.2\%  & 15.9\% 	& 17.9\% \\
   Rubble 			& 97.54\% & 0.16\% 	& 2.3\% \\
   Obstacle race 	& 92.4\%  & 0.15\% 	& 7.45\% \\
 \end{tabular}
\caption{Success rates obtained for the generation of static equilibrium contact configurations for each scenario, rounded to the first decimal. Column 1 indicates 
indicates the rate of contact generation that suceeeded. In the cases where the generation fails, it can be
either a kinematic issue (column 2), or because no contact configuration led to a static equilibrium configuration (column 3). Note that a failure in the contact generation
is not equivalent to a failure of the contact planning algorithm.}
\label{tab:requestpercent}
\quad
\end{table}

>>>>

\subsubsection{HRP-2 -- Car egress (Figure~\ref{fig:car})}
In this scenario inspired from the DRC car egress HRP-2 has to step out of a car.

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/polaris}
  \caption{
           Selected frames from the car egress scenario. }
		   \label{fig:car}
\end{figure}

@@

\subsubsection{Discretization of the guide path} \label{sec:disc}
The discretization step is a user-defined, fixed parameter. The step
has an influence on the output of the planner: if too large steps are taken,
the planner may fail since we impose the constraint that only one contact change might occur
between two consecutive steps. On the other hand, a small step will not impact the success rate of the planner, 
but may generate unnecessary states. In most scenarios the torso of HRP-2 moves about 15 cm between two postures, but only 3 cm
for the car egress scenario to handle the geometry of the car.
For future work, we would like to automatically adapt the size of the discretization step to the complexity of the environment.

@@

\begin{table}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{35pt} | >{\centering\arraybackslash}m{35pt} | c}
  &  Equilibrium success rate & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs 	& 99.5\%  & 0.1\% 	& 0.4\% \\
   Standing up 		& 87.8\%  & 6.1\% 	& 6.1\% \\
   Car egress 		& 66.2\%  & 15.9\% 	& 17.9\% \\
   Rubble 			& 97.54\% & 0.16\% 	& 2.3\% \\
   Obstacle race 	& 92.4\%  & 0.15\% 	& 7.45\% \\
 \end{tabular}
\caption{Success rates obtained for the generation of static equilibrium contact configurations for each scenario, rounded to the first decimal. Column 1 indicates 
indicates the rate of contact generation that succeeded. In the cases where the generation fails, it can be
either a kinematic issue (column 2), or because no contact configuration led to a static equilibrium configuration (column 3). Note that a failure in the contact generation
is not equivalent to a failure of the contact planning algorithm.}
\label{tab:requestpercent}
\quad
\end{table}
